

#loads in the spreadsheet and select certian indicators as factors
```{r}
library(readxl)
worksheet <- read_excel("~/2yeardatafullwithtablesclassandemition.xlsx", 
    col_types = c("numeric", "blank", "numeric", 
        "blank", "numeric", "blank", "numeric", 
        "blank", "blank", "numeric", "numeric", 
        "blank", "text", "numeric", "blank", 
        "blank", "blank", "blank", "numeric", 
        "blank", "numeric", "blank", "numeric", 
        "blank", "numeric", "numeric", "blank", 
        "blank", "text", "blank", "text", 
        "numeric", "numeric"))
View(worksheet)
worksheet$DayOfWeek = as.factor(worksheet$DayOfWeek)
worksheet$`Source V2` = as.factor(worksheet$`Source V2`)
worksheet$has_link = as.factor(worksheet$has_link)
worksheet$has_picture = as.factor(worksheet$has_picture)
worksheet$`Has Hashtag?` = as.factor(worksheet$`Has Hashtag?`)
worksheet$Hour = as.factor(worksheet$Hour)
worksheet$url_shortended = as.factor(worksheet$url_shortended)
worksheet$`Has Mention` = as.factor(worksheet$`Has Mention`)
worksheet$imp_word_count = as.factor(worksheet$imp_word_count)
worksheet$url_shortended = as.factor(worksheet$url_shortended)
worksheet$Month = as.factor(worksheet$Month)
worksheet$Class = as.factor(worksheet$Class)
worksheet$`Sentiment per Document` = as.factor(worksheet$`Sentiment per Document`)

str(worksheet)
levels(worksheet$`Sentiment per Document`)
levels(worksheet$`Source V2`)
summary(worksheet$`Sentiment per Document`)

```



#sets the seed 

```{r}

set.seed(101) 


```

#Creates a scatter plot matrix of all correlations
```{r}





#(worksheet,main = "Scatterplot Matrix")
png(file="scatterplot.png", width = 1000, height = 700)
pairs(~., data=worksheet,main = "Scatterplot Matrix")
dev.off()






```


#Prints the linear model out for retweets 
```{r}
BigModelRT=lm(Retweets~.,data=worksheet)

summary(BigModelRT)




```

#Prints the linear model out for likes 

```{r}

BigModelFav=lm(favorites~.,data=worksheet)

summary(BigModelFav)




```








#Smaller Linear model with only certain predictors for Retweets
```{r}



tweetmodelRT= lm(Retweets~has_link+`Has Hashtag?`+DayOfWeek+url_shortended+Class+`Sentiment per Document`+imp_word_count,data=worksheet)


summary(tweetmodelRT)

```

#histograms and plots of the models for Retweets

```{r}

hist(tweetmodelRT$residuals)
hist(BigModelRT$residuals)

plot(tweetmodelRT)
plot(BigModelRT)


```

#Smaller Linear model with only certain predictors for Likes

```{r}



tweetmodelFav=lm(favorites~has_link+has_picture+`Source V2`+`Has Hashtag?`+`Has Mention`+DayOfWeek+Hour+url_shortended+Class+`Sentiment per Document`+imp_word_count,data=worksheet)


summary(tweetmodelFav)

```


```{r}

hist(tweetmodelFav$residuals)
hist(BigModelFav$residuals)



plot(tweetmodelFav)
plot(BigModelFav)

```




#creates a fake tweet and predicts how many Retweets and likes it gets 
```{r}
#Retweets,has_link,Length of Filtered Text,has_picture,Number of Hashtags,Has hashtag,Source V2,favorites,Month,DayOfWeek,Hour,Has mention,Number of mentions,url_shortended,imp_char_count,Class,Sentiment,imp_word_count


input=c(1,1,99,1,1,1,'Hutch',0,2,6,11,1,2,'No',0,"Health Advice","Positive",0)
newdata=rbind(worksheet,input)

#fixes the data type changes
#check type with cbind(lapply(worksheet, class), lapply(newdata, class))
newdata$Retweets=as.numeric(newdata$Retweets)
newdata$favorites=as.numeric(newdata$favorites)
newdata$`Length of Filtered Text` = as.numeric(newdata$`Length of Filtered Text`)
newdata$`Number of Hashtags` = as.numeric(newdata$`Number of Hashtags`)
newdata$`Number of Mentions` = as.numeric(newdata$`Number of Mentions`)
newdata$imp_char_count=as.numeric(newdata$imp_char_count)


  
predictedrt=predict.lm(BigModelRT,newdata=newdata,interval="prediction",level=0.9)

tail(predictedrt,n=1)


#summary(tweetmodelv1)
# drop1(tweetmodelv1,~.,test="F")

```

predictedFav=predict.lm(BigModelFav,newdata=newdata,interval="prediction",level=0.9)

tail(predictedFav,n=1)



#creates a boxplot of class VS Retweets
```


```{r}
library(ggplot2)
png(file="boxplots.png", width = 1000, height = 700)

ggplot(worksheet, aes(x = `Class`, y = `Retweets`)) +
  geom_boxplot(fill = "black", colour = "red") +
  scale_x_discrete() + xlab("Class") +
  ylab("Retweets")
dev.off()




```

